\vspace{5em}On Evaluating Adversarial Robustness

### 2019-04-25 paper.tex
typo

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success and adversarial loss versus the number of
iterations.
%
This plots should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does. Plotting the adversarial loss is often more useful than plotting the attack success rate, as the former has a finer granularity and may reveal that the attack is still making progress even though the success rate seems to have plateaued.
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example from one second to ten seconds does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent, as well as many different random restarts (to avoid converging to sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}).

>>>>

On at least a few inputs, confirm
that the number of iterations of gradient descent being performed is
sufficient by plotting the attack success and adversarial loss versus the number of
iterations.
%
These plots should eventually plateau; if not, the attack
has not converged and more iterations can be used until
it does. Plotting the adversarial loss is often more useful than plotting the attack success rate, as the former has a finer granularity and may reveal that the attack is still making progress even though the success rate seems to have plateaued.
The number of
iterations necessary is generally inversely proportional to step size and
proportional to distortion allowed.
%
Dataset complexity is often related.

@@

There are few reasonable threat models under which an attacker can
compute 100 iterations of gradient descent, but not 1000. As stated in~\cite{athalye2018obfuscated}, merely increasing the time it takes an adversary to find an adversarial example (e.g., from one second to ten seconds) does not constitute an increase in robustness.
%
Because the threat model must not constrain the approach an
attacker takes, it is worth evaluating against a strong attack
with many iterations of gradient descent, as well as many different random restarts (to avoid converging to sub-optimal local minima~\citep{madry2017towards,mosbach2018logit}).
